\documentclass{article}
\usepackage[backend=biber,
style=numeric,
sorting=none,
isbn=false,
doi=false,
url=false,
]{biblatex}\addbibresource{bibliography.bib}

\usepackage{txfonts}
\usepackage{enumitem}
\usepackage[svgnames,table]{xcolor}
\usepackage{longtable}
\usepackage{setspace}
\usepackage[hidelinks]{hyperref}
\usepackage[a4paper,left=1.5cm,right=1cm,top=1cm,bottom=0.1cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

%XXXXXXXXXXXX Set Depths for Sections XXXXXXXXXXXXXX

\setcounter{tocdepth}{5}
\setcounter{secnumdepth}{5}

%XXXXXXXXXXXX Set Depths for Nested Lists created by \begin{enumerate} XXXXXXXXXXXXXX

\renewlist{itemize}{itemize}{2}
       \setlist[itemize]{label=$\cdot$, itemsep=0.5pt}
       \setlist[itemize,1]{label=\textbullet, itemsep=0.5pt}
       \setlist[itemize,2]{1abel=$\circ$, itemsep=0.5pt}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    linkbordercolor=blue,
}
\urlstyle{same}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{longtable}{p{0.00in}p{0.00in}p{0.0in}p{0.00in}p{0.00in}}
\multicolumn{3}{p{\dimexpr3.00in+4\tabcolsep\relax}}{{\fontsize{16pt}{19.2pt}\selectfont
    \textbf{Ravil Galeyev}}
    \href{https://www.linkedin.com/in/ravil-galeyev-9a7540102}{LinkedIn},
    \href{http://stackoverflow.com/story/dehasi}{StackOverflow}
} &
\multicolumn{1}{l}{xxxxxxxx@gmail.com} &
\multicolumn{1}{l}{+31 123 456 789} \\

\multicolumn{5}{p{\dimexpr7.00in+8\tabcolsep\relax}}{
    Amsterdam, Netherlands. Citizenship: Kazakhstan (Kennismigrant).
\par} \\

\multicolumn{5}{p{\dimexpr7.00in+8\tabcolsep\relax}}{
    \textbf{Key words:} Java, Spring, SQL, Docker, Jenkins, Eclipse MAT, Apache Ignite ML
\par} \\

\multicolumn{5}{c}{\textbf{Work experience}} \\

\multicolumn{2}{p{\dimexpr1.00in+2\tabcolsep\relax}}{January 2019 \par Amsterdam,\par Netherlands} &
\multicolumn{3}{p{\dimexpr5.85in+4\tabcolsep\relax}}{\href{https://degiro.nl}{DeGiro} (acquired by Flatex)
Position: \textbf{Java developer} \par
Developing the trading platform. Implementing various tasks,
\par mostly related to client data, instant payments and reporting;
\begin{itemize}
    \item Led client data and payments integration with Flatex during acquisition;
    \item Built a monorepo and CI pipeline, fixed bugs in
          \href{https://github.com/apache/maven/pull/347}{maven}
           and  \href{https://github.com/mojohaus/flatten-maven-plugin/pull/152}{maven-flatten-plugin};
    \item Developed a DSL for test data generation;
    \item Dockerized test envionmets;
    \end{itemize}
    Made a \href{https://compscicenter.ru/courses/practical-minimum/}{course} in Computer Science Center.
\par} \\

\multicolumn{2}{p{\dimexpr1.00in+2\tabcolsep\relax}}{September 2017 -- \par December 2018 \par Krakow, Poland} &
\multicolumn{3}{p{\dimexpr5.85in+4\tabcolsep\relax}}{\href{https://grandparade.co.uk/}{Grand Parade} (part of William Hill company)
Position: \textbf{Java developer} \par
Developing Microservices for the betting platform:
\begin{itemize}
    \item Led a backend team for CRM-ish app for betting shops across the UK;
    \item Automated documentation generation;
    \item Established API contracts between front- and backend;
    \item Refactored legacy services, increased test coverage;
\end{itemize}
    Started \href{https://github.com/apache/ignite/commits?author=dehasi}{contributing} to open source.
\par} \\

\multicolumn{2}{p{\dimexpr1.00in+2\tabcolsep\relax}}{August 2016 -- \par August 2017 \par Krakow, Poland} &
\multicolumn{3}{p{\dimexpr5.85in+4\tabcolsep\relax}}{\href{https://www.epam.com/}{Epam} (Google onsite)
Position: \textbf{Java developer} \par \par
Contract software engineer at Google (under NDA)
\par}\\

\multicolumn{2}{p{\dimexpr1.00in+2\tabcolsep\relax}}{June 2015 -- \par August 2016 \par St. Petersburg, \par Russia} &
\multicolumn{3}{p{\dimexpr5.85in+4\tabcolsep\relax}}{\href{https://www.t-systems.com/ru/en}{T-Systems} (Swiss Federal Railways SBB CFF FFS)
Position: \textbf{Java developer} \par
Development a ticket sailing system for public transport. Mostly worked in data-team.
\begin{itemize}
    \item Created and maintained tools for data releases generation and validation;
    \item Created a tool for special routes importing;
    \item Created a tool for automating tests-scripts creation;
    \item Maintained a database and migrated data;
\end{itemize}
\par} \\

\multicolumn{2}{p{\dimexpr1.00in+2\tabcolsep\relax}}{2012 -- 2015 \par St. Petersburg,\par Russia} &
\multicolumn{3}{p{\dimexpr5.85in+4\tabcolsep\relax}}{Russain Academy of Science\par \href{http://iairas.ru/en/}{Institute for Analytical Instrumentation}
Position: \textbf{C/C$\#$ developer} \par
\begin{itemize}
    \item Developed a DSL for programming genetic experiments;
    \item Developing firmware, for PCR and DNA analysis devices, based on ARM processors;
    \item Developing software on Windows and Linux for device control.
\end{itemize}
} \\

\multicolumn{5}{c}{\textbf{Internships}} \\

\multicolumn{2}{p{\dimexpr1.00in+2\tabcolsep\relax}}{2016 (spring) \par St. Petersburg} &
\multicolumn{3}{p{\dimexpr5.85in+4\tabcolsep\relax}}{\href{https://www.jetbrains.com/}{JetBrains} (Java intern) \par
    Groovy \href{https://github.com/dehasi/groovy-dc}{decompilator} development.
} \\

\multicolumn{2}{p{\dimexpr1.00in+2\tabcolsep\relax}}{2015 (spring) \par St. Petersburg} &
\multicolumn{3}{p{\dimexpr5.85in+4\tabcolsep\relax}}{\href{https://yandex.com/company/}{Yandex} (Java intern) \par
    Internal web application development.
} \\

\multicolumn{5}{c}{ \textbf{Education}} \\

\multicolumn{2}{p{\dimexpr1.00in+2\tabcolsep\relax}}{2008 -- 2014} &
\multicolumn{3}{p{\dimexpr5.85in+4\tabcolsep\relax}}{Saint Petersburg Electrotechnical
   University $"$\href{https://etu.ru/en/university/}{LETI}$"$. Master degree in Computer Technology
} \\

\multicolumn{2}{p{\dimexpr1.00in+2\tabcolsep\relax}}{2014 -- 2016} &
\multicolumn{3}{p{\dimexpr5.85in+4\tabcolsep\relax}}{Saint Petersburg
    \href{https://compscicenter.ru/students/714/}{Computer Science Center} Specialization: Data mining
} \\

\multicolumn{2}{p{\dimexpr1.00in+2\tabcolsep\relax}}{2017 -- 2018} &
\multicolumn{3}{p{\dimexpr5.85in+4\tabcolsep\relax}}{Coursera:
\href{https://www.coursera.org/account/accomplishments/specialization/certificate/HEKRFB8RMKUD}{Parallel, Concurrent, and Distributed Programming in Java}\ $\vert$
    \href{https://www.coursera.org/account/accomplishments/verify/3YL6SFFSLZCT}{Machine Learning} \par
    \href{https://www.coursera.org/account/accomplishments/specialization/certificate/GAR3792UCR6W}{Functional Programming in Scala}
\par} \\

\multicolumn{5}{p{\dimexpr7.00in+8\tabcolsep\relax}}{
    \textbf{Open Source:}
    \href{https://github.com/apache/ignite/commits?author=dehasi}{Apache Ignite ML},
    \href{https://github.com/mojohaus/flatten-maven-plugin/commits?author=dehasi}{flatten-maven-plugin},
    \href{https://github.com/apache/maven/pull/347}{maven},
    \href{https://github.com/dehasi/zeliba}{ZeLiba}
\par} \\

\multicolumn{5}{p{\dimexpr7.00in+8\tabcolsep\relax}}{
    \textbf{Languages:} English, Polish, Russian, a bit of Dutch
} \\

\end{longtable}
\end{document}
