%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}
\usepackage[hidelinks]{hyperref}
\usepackage[svgnames,table]{xcolor}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,
	urlcolor=blue,
	linkbordercolor=blue,
}
\urlstyle{same}

% Set applicant's personal data for header
\name{Ravil Galeyev}
\address{Amsterdam \linebreak blavla \href{https://www.linkedin.com/in/ravil-galeyev-9a7540102}{LinkedIn}}
\contacts{+31 123 456 789 \linebreak xxxxxxx@gmail.com}

\begin{document}

	% Print the header
	\makeheader

	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Java Developer }{\href{https://degiro.nl}{DeGiro} (acquired by Flatex)}{January 2019 -- present}
			Developing the trading platform. Implementing various tasks,
			mostly related to client data, instant payments and reporting;

			\begin{itemize}
				\item Led client data and payments integration with Flatex during acquisition;
				\item Built a monorepo and CI pipeline, fixed bugs in
				\href{https://github.com/apache/maven/pull/347}{maven}
				and  \href{https://github.com/mojohaus/flatten-maven-plugin/pull/152}{maven-flatten-plugin};
				\item Developed a DSL for test data generation;
				\item Dockerized test envionmets;
			\end{itemize}
			Made a \href{https://compscicenter.ru/courses/practical-minimum/}{course} in Computer Science Center.
		\end{cvsubsection}

		\begin{cvsubsection}{Java Developer}{\href{https://grandparade.co.uk/}{Grand Parade} (part of William Hill company)}{September 2017 -- December 2018}
			Developing Microservices for the betting platform:
			\begin{itemize}
				\item Led a backend team for CRM-ish app for betting shops across the UK;
				\item Automated documentation generation;
				\item Established API contracts between front- and backend;
				\item Refactored legacy services, increased test coverage;
			\end{itemize}
			Started \href{https://github.com/apache/ignite/commits?author=dehasi}{contributing} to open source.
		\end{cvsubsection}

		\begin{cvsubsection}{Java developer}{\href{https://www.epam.com/}{Epam}}{August 2016 -- August 2017}
			Contract software engineer at Google (under NDA)
		\end{cvsubsection}

		\begin{cvsubsection}{Java developer}{\href{https://www.t-systems.com/ru/en}{T-Systems}}{June 2015 -- August 2016}
			Development a ticket sailing system for public transport. Mostly worked in data-team.
			\begin{itemize}
				\item Created and maintained tools for data releases generation and validation;
				\item Created a tool for special routes importing;
				\item Created a tool for automating tests-scripts creation;
				\item Maintained a database and migrated data;
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{C,C$\#$ developer}
		{Russiaan Academy of Science \href{http://iairas.ru/en/}{Institute for Analytical Instrumentation}}
		{2012 -- 2015}
			\begin{itemize}
				\item Developed a DSL for programming genetic experiments;
				\item Developing firmware, for PCR and DNA analysis devices, based on ARM processors;
				\item Developing software on Windows and Linux for device control.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Internships}
		\begin{cvsubsection}{Java intern}{\href{https://www.jetbrains.com/}{JetBrains}}{Spring 2016}
			Groovy \href{https://github.com/dehasi/groovy-dc}{decompilator} development.
		\end{cvsubsection}
		\begin{cvsubsection}{Java intern}{\href{https://yandex.com/company/}{Yandex}}{Spring 2015}
			Groovy \href{https://github.com/dehasi/groovy-dc}{decompilator} development.
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Education}
		\begin{cvsubsection}{Saint Petersburg}{Electrotechnical University $"$\href{https://etu.ru/en/university/}{LETI}$"$}{2008 -- 2014}
			Master degree in Computer Technology.
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Multi-User Drawing Tool} (2004). Electronic classroom where multiple users can view and simultaneously draw on a “chalkboard” with each person’s edits synchronized.  C++, MFC
				\item \textbf{Synchronized Calendar} (2003 – 2004). Desktop calendar with globally shared and synchronized calendars, allowing users to schedule meetings with other users.  C\#.NET, SQL, XML
				\item \textbf{Operating System} (2002).  UNIX-style OS with scheduler, file system, text editor and calculator. C
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Additional Experience and Awards}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item \textbf{Instructor (2003 – 2005):} Taught two full-credit Computer Science courses; average ratings of 4.8 out of 5.0.
				\item \textbf{Third Prize, Senior Design Projects:} Awarded 3rd prize for Synchronized Calendar project, out of 100 projects.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item C++; C; Java; Objective-C; C\#.NET; SQL; JavaScript; XSLT; XML (XSD) Schema
				\item Visual Studio; Microsoft SQL Server; Eclipse; XCode; Interface Builder
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

\end{document}
